Quick, Draw! Image Classification

### 2018-12-07 report/draft.tex
updating section 2.1

We use human classification, fully connected neural networks,
and a Convolutional Neural Network (CNN). We discuss the CNN in
more detail than was covered in class so an overview is provided
here.

@@

Google originally collected the data from users by explicitly asking users to
draw objects like forks, hotdogs, etc. The original dataset is 70 GB in size
but Google also provides a simplified version of the dataset- consisting only
of the final images. We used these '.npy' files to train all of our models.
These numpy bitmap files consist of more than 100,000 rows each and 784
features, since they are basically $28 \times 28$ images. Samples of these
images are shown in Figure \ref{fig:quickImages}. The subset of this
dataset sampled varies from experiment to experiment. More details can be
found in the experiments mentioned below.

@@

@@

In order to perform this experiment we built a fully connected neural network
using tensorflow. Our dataset sample selected for this experiment had 10
categories: fish, fork, hotdog, flamingo, airplane, alarm clock, baseball bat,
bicycle, dolphin, elephant. We had 100,000 examples in total, with 10,000
example for each of the aforementioned categories. Our train:test split was
chosen to be 80:20, an industry standard.

@@

There are a number of different optimization methods such as Stochastic
and Batch Gradient descent. In practice, we chose to use a faster variant
of gradient descent called Adam. The Adam optimization is able to use
an exponentially weighted average of the gradients, a technique called
momentum, and then use that gradient to update your weights instead. We
also want to slow down gradient descent in the horizontal direction, a
technique called RMSprop), to reduce oscillations from batch gradient descent.
The Adam optimization method is combining momentum and RMSprop to perform
gradient descent more quickly \cite{DeepLear51:online}.

>>>>

We use human classification, fully connected neural networks,
and a Convolutional Neural Network (CNN). We use more detail to
describe techniques not covered during the course.

This course discussed optimization algorithms such as Stochastic Gradient
Descent ($m =1$) and Batch Gradient Descent ($m=n \text{ obs.}$). Current
best practices for Neural Networks recommend Mini-Batch Gradient Descent
($m = c \text{ batch size}$). In practice, we use the Adam optimization
algorithm due to faster computation time. The Adam optimization algorithm
is able to achieve a speedup due to its combination of two other techniques.

The Adam optimization algorithm takes an exponentially weighted average of
the gradients, a technique called momentum, and then uses that gradient to
update your weights. Secondly, we also want to slow down gradient descent in
the horizontal direction with a technique called RMSprop to reduce
oscillations from batch gradient descent. The Adam optimization method is
combining momentum and RMSprop to perform gradient descent more quickly
\cite{DeepLear51:online}.

@@

Google originally collected the data from users by explicitly asking users to
draw objects like forks, hotdogs, etc \cite{QuickDra91:online}. The original
dataset is 70 GB in size but Google also provides a simplified version of the
dataset- consisting only of the final images \cite{googlecr61:online}. We
used these '.npy' files to train all of our models. These numpy bitmap files
consist of more than 100,000 rows each and 784
features, since they are basically $28 \times 28$ images. Samples of these
images are shown in Figure \ref{fig:quickImages}. The subset of this
dataset sampled varies from experiment to experiment. More details can be
found in the experiments mentioned below.

@@

Our analysis required us to use a subset of this data. Our dataset sample
selected for this experiment had 10 categories: fish, fork, hotdog, flamingo,
airplane, alarm clock, baseball bat, bicycle, dolphin, elephant. We had
100,000 examples in total, with 10,000 example for each of the aforementioned
categories.

@@

In order to perform this experiment we built a fully connected neural network
using tensorflow. Our train:test split was chosen to be 80:20, an industry
standard.

@@
